\documentclass[11pt,a4paper,titlepage]{article}

%%%%%%%%%
%%usees%%
%%%%%%%%%
\usepackage[utf8]{inputenc}
%\usepackage[ngerman]{babel}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{amssymb} 
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{footnote}
\usepackage{caption}
\usepackage{color}



%%%%%%%%%
%%Title%%
%%%%%%%%%
\author{Frederik Zwilling 304314}
\title{Proposal:\\ Bachelorthesis Simulation LLSF with Gazebo}
\begin{document}
\maketitle
\thispagestyle{empty}
\tableofcontents
\newpage
\onehalfspace

%%%%%%%%%
%%Text%%
%%%%%%%%
\abstract{Short describtion}
\section{Introduction}
Autonomous robots are about to play an important role in the future of logistics. They will be able to save time and cost in the industial production process and boost the economy. Especially multi-robot-systems play an important role in this context. Though, the develpoment of these logistic robots can be difficult because the robots have to handle many complex tasks. They have to detect objects, localize themselfs, make a plan of what to do in which order, coordinate with other robots, optimize the workflow, be save for humans and hardware at every time and much more.\\
The key to effective and time saving development of reliable software for robots is siumulation. Simulation makes it possible to virtually test written code fast in different scenarios.This leads to better quality of the software and better performance of the robot. By simulating the behavior of a robot much time can be saved because there is no real robot which has to be set up and the simulation can quickly change between different scenarions. Furthermore it is possible to speed the simulation up or run multiple simulations at once. Simulation also makes testing possible if no real robot is available and can be easily used to compare different versions of the software. For example this can be useful to find unknown parameters like thresholds.\\
The proposed bachelorthesis will work on this area and will develop a simulation environment for the \textit{Logistic League Sponsored by Festo} (LLSF) with the open source simulator \textit{Gazebo} \textcolor{red}{(mulit robot?)}.


\section{Gazebo}
\section{Related Work}
\section{Detail}
\section{Timetable}
\section{Evaluation}
\section{Conclusion}


\end{document}
